\huge {\bold Parallel Algorithms}

### 2024-09-16 Papers/Parallel Aalgorithms/Booklet/PA.tex
add Disclaimer section and add Grading and Evaluation section

@@

@@

>>>>

\usepackage{hyperref}

\usepackage{color}

@@

    In this lecture note, I have documented my personal interpretations and understanding of the material. Please note that there may be inaccuracies, and it is recommended to consult primary and authoritative sources for complete and accurate information. Additionally, I welcome any contributions to improve and refine this note. If you are reading this and would like to offer suggestions, feel free to do so via pull requests on my \href{https://github.com/elprofesorsunny/Master/tree/main/Papers/Parallel%20Aalgorithms/Booklet}{\textcolor{blue}{\bold GitHub}} or by emailing me at \href{mailto:someone@somewhere.com}{\textcolor{blue}{\bold mohammad\_khorshidi@outlook.fr}}.

@@

        The grading structure for this course is as follows, with students expected to earn their grades based on the criteria outlined below:

            \item {\bold Presentation:} 4 points will be awarded for presenting and explaining a paper related to one aspect of parallelization, accompanied by its relevant implementation.

            \item {\bold Midterm Exam:} 4 points will be given for the midterm exam.

            \item {\bold Final Exam:} 12 points will be awarded for the final exam.

        Additionally, students are expected to attend all classes and give due attention to the assignments that will be provided throughout the semester.
